$\,$ \\ $\,$ \\ Preliminary results for Video NL-Bayes

### 2016-07-20 doc/201505_vnbayes3d/slides_vnlb3d.tex

\multipleframe
\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}

@@

	\begin{center}
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_army.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_mequon.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_walking.eps}
	\end{center}

	\begin{center}
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_army.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_mequon.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_walking.eps}
	\end{center}

	\begin{center}
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_army.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_mequon.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_walking.eps}
	\end{center}

\multipleframe
\begin{frame}{Running time tables - rank vs. number of patches, stage 2}

	\begin{center}
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_army.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_mequon.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_walking.eps}
	\end{center}

\begin{frame}{Running time tables - rank vs. number of patches, stage 2}

	\begin{center}
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_army.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_mequon.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_walking.eps}
	\end{center}

\begin{frame}{Running time tables - rank vs. number of patches, stage 2}

	\begin{center}
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_army.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_mequon.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_walking.eps}
	\end{center}

@@

\multipleframe
\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}

@@

	\begin{center}
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_army.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_mequon.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_walking.eps}
	\end{center}

	\begin{center}
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_army.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_mequon.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_walking.eps}
	\end{center}

	\begin{center}
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_army.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_mequon.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_walking.eps}
	\end{center}

\multipleframe
\begin{frame}{Running time tables - rank vs. number of patches, stage 1}

	\begin{center}
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_army.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_mequon.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_walking.eps}
	\end{center}

\begin{frame}{Running time tables - rank vs. number of patches, stage 1}

	\begin{center}
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_army.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_mequon.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_walking.eps}
	\end{center}

\begin{frame}{Running time tables - rank vs. number of patches, stage 1}

	\begin{center}
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_army.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_dogdance.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_evergreen.eps}\\
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_mequon.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_walking.eps}
	\end{center}

\begin{frame}{Conclusions - rank vs. number of patches, stage 1}
	\begin{itemize}\itemsep=2cm
		\item We can improve the basic estimate, but we cannot improve the final estimate.
		\item The qualitative behaviour depends on the noise level.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Conclusions - rank vs. number of patches, stage 1}
	Based on this observations, we propose the following parameters:
	\[r = 160\quad\quad n_{\text{sim}} = \max(15\sigma,cr).\]

	Notes:
	\begin{itemize}\itemsep=.3cm
		\item The rank $r$ could be smaller, but there is not much difference in
			computational time nor in PSNR. We therefore choose a more
			conservative higher rank.
		\item The linear relation $n_{\text{sim}} = 15\sigma$ comes from observing that
			for good results are obtained at
			\begin{center}
				\begin{tabular}{l | c c c}
					$\sigma$         &  10 &  20 &  40 \\ 
					$n_{\text{sim}}$ & 150 & 300 & 600 
				\end{tabular}
			\end{center}
		\item $c\geqslant1$ is a constant multiplying the rank. When $15\sigma$
			is too small, we ignore the linear relation and take a fixed number of
			patches which depend on the rank. \textbf{We should do more experiments
			to determine an appropriate value for $c$. For the moment, we will choose
         5.} With this choice,
			\[
				n_{\text{sim}} =
				\left\{
				\begin{array}{l l}
					15\sigma & \text{if }\sigma \geqslant r/3\\
					5r       & \text{if }\sigma < r/3
				\end{array}
				\right.
			\]
			For $r = 16$, $5r = 80$ and $r/3 \approx 5.33$.
	\end{itemize}
\end{frame}

\restoreframe

>>>>

@@

%\multipleframe
%\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_walking.eps}
%	\end{center}
%\end{frame}
%
%\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_walking.eps}
%	\end{center}
%\end{frame}
%
%\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_walking.eps}
%	\end{center}
%\end{frame}
%\restoreframe
%
%\multipleframe
%\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_walking.eps}
%	\end{center}
%\end{frame}
%
%\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_walking.eps}
%	\end{center}
%\end{frame}
%
%\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_walking.eps}
%	\end{center}
%\end{frame}
%\restoreframe

\begin{frame}{Average PSNR and running time - rank vs. number of patches, stage 2}
	\begin{center}
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_average.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_average.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_average.eps}\\
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_average.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_average.eps}%
		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_average.eps}\\
	\end{center}
\end{frame}

@@

@@

%\multipleframe
%\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_walking.eps}
%	\end{center}
%\end{frame}
%
%\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_walking.eps}
%	\end{center}
%\end{frame}
%
%\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_walking.eps}
%	\end{center}
%\end{frame}
%
%\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_walking.eps}
%	\end{center}
%\end{frame}
%
%\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_walking.eps}
%	\end{center}
%\end{frame}
%
%\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_walking.eps}
%	\end{center}
%\end{frame}
%\restoreframe

\begin{frame}{Average PSNR and running time - rank vs. number of patches, stage 1}
	\begin{center}
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_average.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_average.eps}%
		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_average.eps}\\
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_average.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_average.eps}%
		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_average.eps}\\
	\end{center}
\end{frame}

\multipleframe
\begin{frame}{Conclusions - rank vs. number of patches, stage 1}
	\begin{itemize}\itemsep=2cm
		\item We can improve the basic estimate, but we cannot improve the final estimate.
		\item The qualitative behaviour depends on the noise level.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Conclusions - rank vs. number of patches, stage 1}
	Based on these observations, we propose the following parameters:
	\[r = 160\quad\quad n_{\text{sim}} = \max(15\sigma,cr).\]

	Notes:
	\begin{itemize}\itemsep=.3cm
		\item The rank $r$ could be smaller, but there is not much difference in
			computational time nor in PSNR. We therefore choose a more
			conservative higher rank.
		\item The linear relation $n_{\text{sim}} = 15\sigma$ comes from observing that
			for good results are obtained at
			\begin{center}
				\begin{tabular}{l | c c c}
					$\sigma$         &  10 &  20 &  40 \\ 
					$n_{\text{sim}}$ & 150 & 300 & 600 
				\end{tabular}
			\end{center}
		\item $c\geqslant1$ is a constant multiplying the rank. When $15\sigma$
			is too small, we ignore the linear relation and take a fixed number of
			patches which depend on the rank. \textbf{We should do more experiments
			to determine an appropriate value for $c$. For the moment, we will choose
         5.} With this choice,
			\[
				n_{\text{sim}} =
				\left\{
				\begin{array}{l l}
					15\sigma & \text{if }\sigma \geqslant r/3\\
					5r       & \text{if }\sigma < r/3
				\end{array}
				\right.
			\]
			For $r = 16$, $5r = 80$ and $r/3 \approx 5.33$.
	\end{itemize}
\end{frame}
\restoreframe

\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}

	We set the following parameters fixed, and spatial search region and the
	spatial pach size in the second step. We also vary the rank in the second
	step.

	\begin{center}
	\begin{tabular}{l | c c | c c | c c }
		& \multicolumn{2}{c|}{$\sigma = 10$} 
		& \multicolumn{2}{c|}{$\sigma = 20$} 
		& \multicolumn{2}{c}{$\sigma = 40$} \\
		                            & 1st  & 2nd  & 1st  & 2nd  & 1st  & 2nd \\\hline\hline
		Patch size (spatial)        &  5   &      &  5   &      &  5   &     \\
		Patch size (temporal)       &  4   &   4  &  4   &   4  &  4   &   4 \\
		Number of patches           & 150  & 160  & 300  & 160  & 600  & 160 \\
		Rank of cov. matrix         & 16   &      & 16   &      & 16   &     \\
		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
		Spatial search window       & 13   &      & 37   &      & 37   &     \\
		Temporal search range       & 5    & 5    & 5    & 5    & 5    & 5   \\\hline
	\end{tabular}
	\end{center}

%\multipleframe
%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 10$ and $r = 16$.
%	\end{center}
%\end{frame}
%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 10$ and $r = 32$.
%	\end{center}
%\end{frame}
%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 10$ and $r = 64$.
%	\end{center}
%\end{frame}
%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 20$ and $r = 16$.
%	\end{center}
%\end{frame}
%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 20$ and $r = 32$.
%	\end{center}
%\end{frame}
%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 20$ and $r = 64$.
%	\end{center}
%\end{frame}
%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 40$ and $r = 16$.
%	\end{center}
%\end{frame}
%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 40$ and $r = 32$.
%	\end{center}
%\end{frame}
%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_army.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 40$ and $r = 64$.
%	\end{center}
%\end{frame}
%\restoreframe

%\multipleframe
%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 10$ and $r = 16$.
%	\end{center}
%\end{frame}
%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 10$ and $r = 32$.
%	\end{center}
%\end{frame}
%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 10$ and $r = 64$.
%	\end{center}
%\end{frame}
%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 20$ and $r = 16$.
%	\end{center}
%\end{frame}
%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 20$ and $r = 32$.
%	\end{center}
%\end{frame}
%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 20$ and $r = 64$.
%	\end{center}
%\end{frame}
%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 40$ and $r = 16$.
%	\end{center}
%\end{frame}
%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_walking.eps}
%	\end{center}
%	\begin{center}
%	Results for $\sigma = 40$ and $r = 32$.
%	\end{center}
%\end{frame}
%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
%	\begin{center}
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_army.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_dogdance.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_evergreen.eps}\\
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_mequon.eps}%
%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_walking.eps}
%	\end{center}
%	\begin{center}
